# Task 359959

We present the results of our analysis of `task 359959` with the different selection set splits used in our study.

```{r task-359959-data, echo=TRUE}
task_data <- filter(results, task_id == 359959)
```


## Testing set accuracy

```{r task-359959-test-05-perf, echo=TRUE, out.width="100%"}
test_plot(task_data)
```

Summary statistics for the testing performance of the different validation methods used:
```{r task-359959-test-05-sum, echo=TRUE, out.width="100%"}
test_results_summary(task_data)
```

The permutation test revealed that the results are:
```{r task-359959-test-05-pv, echo=TRUE, out.width="100%"}
perm_test_maxt(x=filter(task_data, validation == 'compressed')$testing_performance,
                y=filter(task_data, validation == 'aggregated')$testing_performance,
                z=filter(task_data, validation == 'unaggregated')$testing_performance,
                alternative = "two.sided",
                n_perm = 10000,
                seed = seed_offset + 8, x_name = 'com', y_name = 'agg', z_name = 'una')
```

## Validation set accuracy

```{r task-359959-select-05-perf, echo=TRUE, out.width="100%"}
selection_plot(task_data)
```

Summary statistics for the testing performance of the different validation methods used:
```{r task-359959-select-05-sum, echo=TRUE, out.width="100%"}
selection_results_summary(task_data)
```

The permutation test revealed that the results are:
```{r task-359959-select-05-pv, echo=TRUE, out.width="100%"}
perm_test_maxt(x=filter(task_data, validation == 'compressed')$training_performance,
                y=filter(task_data, validation == 'aggregated')$training_performance,
                z=filter(task_data, validation == 'unaggregated')$training_performance,
                alternative = "two.sided",
                n_perm = 10000,
                seed = seed_offset + 9, x_name = 'com', y_name = 'agg', z_name = 'una')
```